---
title: "Answers"
author: "Amit Levinson"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, messages = FALSE)
```

# answers
A repository containing answers for questions in forums.  

You might find discrepancies between the number of times requested in the question and my response. This is mainly for ease of printing.

<details>
  <summary> 
   How can I iterate over every column in my dataframe and calculate a t.test between half of the elemnts (e.g. 1:50 vs 51:100) (10/24/2022)
  </summary>

```{r ttest-part-of-column}
library(purrr)
library(broom)

dat <- data.frame(
  col1 = sample(c(1:100), size = 100, replace = T),
  col2 = sample(c(1:100), size = 100, replace = T),
  col3 = sample(c(1:100), size = 100, replace = T)
)

calculate_ttest <- function(column) {
  t.test(column[50:100], column[1:49], alternative= "less", paired=FALSE, mu=0, conf.level = 0.9, var.equal = TRUE) |>
    broom::tidy() 
}

dat %>% 
  map_dfr(calculate_ttest, .id = 'columnname')
```
</details>




<details>
  <summary> 
  How can we generate ~50 formulas to pass onto a model from a given set of variables? ** 
  </summary>
```{r multiple-formulas}
library(dplyr)
library(purrr)
library(broom)

mtcars_vars <- names(mtcars)

# Generate possible formulas
mtcars_formulas <- expand.grid(mtcars_vars,mtcars_vars,mtcars_vars) %>% 
  filter(Var1 != Var2, Var2 != Var3, Var1 != Var3) %>% 
  sample_n(10)

# Function to create formulas
f <- function (Var1, Var2, Var3) paste(Var1, paste(Var2, Var3, sep = " + "), sep = " ~ ")

formulas <- mtcars_formulas %>%
  pmap_chr(f)

head(formulas)

# Iterate across the formulas and tidy the output with formula as name
models <- map(formulas, ~ lm(., data = mtcars)) %>% 
  set_names(formulas) %>% 
  map_dfr(tidy, .id = ".x")

# Output
models
```
  
</details>



<details>
  <summary> 
  The categories on the X-axis are too condensed and overflow, can we expand them to more than one row? 
  </summary>
```{r ggplot-long-categories}
library(ggplot2)

# Fake data
dat <- data.frame(
category = sample(c(stringr::sentences[1:3], stringr::words[1:4]), size = 100, replace = T)
)

# Option 1 - Category to y axis instead of splitting
p1 <- ggplot(dat) +
geom_bar(aes(y = category)) +
labs(title = "Put the category on the Y-axis")

# Option 2: Stringr::str_wrap
p2 <- ggplot(dat) +
geom_bar(aes(x = stringr::str_wrap(category, 15))) +
labs(title = "use stringr:str_wrap(variable, 15)")
```

</details>


<details>
  <summary> 
  I have X classes (groups) and would like to run a t-test for groups within each class separately
  </summary>
```{r}
library(ggplot2)
library(dplyr)
library(broom)

mtcars %>%
group_by(gear) %>%
summarize(t.test(mpg , cyl, data = cur_data()) %>% tidy())

# Using Purrr & unnest
library(purrr)
library(tidyr)

mtcars %>%
group_nest(gear) %>%
summarise(ttest = map(data, ~ (t.test(x = .$mpg , y = .$cyl, data = .x)))) %>%
mutate(ttest = map(ttest, tidy)) %>%
unnest(ttest)
```

</details>


<details>
  <summary> 
  How can you randomly sample 100 values with replacement from a vector and calculate an IQR, 10000 times?
  </summary>

```{r samples-and-iqr}
# Fake data
vec <- 1:100

# Option 1: Functional
calc_iqr <- function() {
    inner_vec <- sample(vec, size = 100, replace = T)
    IQR(inner_vec)
}

values_a <- replicate(100, expr = calc_iqr())

# Output ------------------------------------------------------------------
values_a

# Option 2: For loop
values_b <- vector(mode = "numeric", length = 100)

output <- for (i in 1:100) {
  inner_vec <- sample(vec, size = 100, replace = T)
  values_b[[i]] <- IQR(inner_vec)
}

# Output ------------------------------------------------------------------
values_b
```
</details>




